Molecular dynamics simulation of synchronization in driven particles

### 2020-11-20 manuscript/manuscript_ajp_2020.tex
added code with verbatim command

@@

%\begin{pyverbatim}
##########################################################
#ADD CONTOUR PLOT
##########################################################
def add_contour(ax,L,N,corrugated = True):
    '''
    Hardwired to color in the quasi1D potential to contain 
    the particles in a trough.  
    Can also add the washboard/corrugated substrate.

@@

    #ax1.set_xticks([])
    #ax1.set_yticks([])
    return
 %   \end{pyverbatim}

>>>>

\begin{verbatim}
##########################################################
#ADD CONTOUR PLOT
##########################################################
def add_contour(ax,L,N,corrugated = True):
    '''
    Hardwired to color in the quasi1D potential to contain 
    the particles in a trough.  
    Can also add the washboard/corrugated substrate.

    #ax1.set_xticks([])
    #ax1.set_yticks([])
    return
\end{verbatim}

@@

\begin{verbatim}
##########################################################
#ADD CONTOUR PLOT
##########################################################
def add_contour(ax,L,N,corrugated = True):
    '''
    Hardwired to color in the quasi1D potential to contain 
    the particles in a trough.  
    Can also add the washboard/corrugated substrate.

@@

    #ax1.set_xticks([])
    #ax1.set_yticks([])
    return
\end{verbatim}
